Synthesizing Symmetric Lenses

### 2019-01-29 papers/SymmetricLenses/main.tex
Checkpoint

  \centering
  \resizebox{\columnwidth}{!}{%
    \begin{tabular}{|>{\columncolor{vlightyellow}}c|>{\columncolor{vlightgreen}}c|}
      \hline
      Management's data & HR's data \\
      \hline
      \listingA & \listingB \\
      \hline
      \cellcolor{lightyellow}Management's type & 
      \cellcolor{lightgreen} HR's type\\
      \hline
      \cellcolor{lightyellow}\listingC & \cellcolor{lightgreen}\listingD \\
      \hline
    \end{tabular}
  }
  \caption{Hypothetical example data files and corresponding regular expressions
  used by management and HR at a US company to represent employee salaries and health
  insurance providers, respectively. \bcp{The colors are a bit loud,
    especially since there is so little color elsewhere.}
  %
  \bcp{Suggest replacing ``Name,Company'' with ``First Last, Company'' (too
    many ``name''s flying around)}
  %
  \bcp{More substantially, thinking about this example makes me wonder about
    a whole different way of specifying simple symmetric lenses: rather than
    just giving corresponding source and target pairs, could we give triples
    of the form ``new source / old target / new target'' and ``new target /
    old source / new source''?  I know these would be a bit more work to
    write, but they would also give the synthesis procedure way more
    information to work with---it seems to me it should be able to do much
    less guessing about where things are disconnected.  Would this allow us
    to drop all the information theory?  Or would we still need it?  (In
    retrospect, this seems like a fairly obvious thing to try, so it seems
    important to try it and report on how it performs relative to what we
    propose here...)}  }
  \label{fig:minimized-representations}
\end{figure}

@@

\subsection{Simple Symmetric Lenses}
Semantically, a simple symmetric lens between sets $X$ and
$Y$ comprises four functions that collectively satisfy four
``round-tripping'' laws:

%\begin{enumerate}
%\item $\CreateR \OfType \Regex \rightarrow \RegexAlt$
%\item $\CreateL \OfType \RegexAlt \rightarrow \Regex$
%\item $\PutR \OfType \Regex \rightarrow \RegexAlt \rightarrow \RegexAlt$
%\item $\PutL \OfType \RegexAlt \rightarrow \Regex \rightarrow \Regex$
%\end{enumerate}
\vskip 1.5ex
\begin{minipage}[c]{.3\textwidth}
\begin{gather}
 \tag{1}
 \mbox{$\CreateR \OfType X \rightarrow Y$}\\
 \tag{2}
 \mbox{$\CreateL \OfType Y \rightarrow X$}\\
 \tag{3}
 \mbox{$\PutR \OfType X \rightarrow Y \rightarrow Y$}\\
 \tag{4}
 \mbox{$\PutL \OfType Y \rightarrow X \rightarrow X$}
\end{gather} 
\end{minipage} 
\begin{minipage}[c]{.6\textwidth}
\begin{align}
  \tag{\CreatePutRL}
  \PutLOf{(\CreateROf{x})}{x} = x\\
  \tag{\CreatePutLR}
  \PutROf{(\CreateLOf{y})}{y} = y\\
  \tag{\PutRL}
  \PutLOf{(\PutROf{x}{y})}{x} = x\\
  \tag{\PutLR}
  \PutROf{(\PutLOf{y}{x})}{y} = y
\end{align}
\end{minipage} 
\vskip 1ex
\bcp{I want less space between the put/create laws and their names.}
\noindent
The two \KW{create} functions are used to propagate shared information and
fill in default values when introducing new data (\EG, the ``unk'' salary
entry is added\bcp{is added by what?  A create function, I guess, but the
  connection is not clear} alongside the name to the management file when HR inserts a
new employee). The two \KW{put} functions propagate edits from one format to
the other by combining a new value from one with an old value from the
other.  The round-tripping laws guarantee that pushing an ``un-edited''
value from one side (the result of a put or create) back through a lens in
the other direction will get back to exactly where we began.  \bcp{That
  paragraph seems likely to be quite opaque to any reader that is not
  already familiar with (symmetric) lenses.  How about a concrete example?}

@@

We do not expect programmers to define simple symmetric lenses by
writing four functions by hand and showing they satisfy the round-tripping
laws.  Instead, we provide a set of combinators---a domain-specific
language---for building complex lenses from simpler ones.  Such languages
have been given for building lenses over many different kinds of data,
including database relations~\cite{BohannonPierceVaughan} and algebraic data
types~\cite{symmetric-lenses}\bcp{and what else? graphs, etc.?}.  We focus
here on combinators for defining lenses between string data formats
described by regular expressions.

If $\BRegex$ and $\BRegexAlt$ are regular expressions, then
\lstinline{$\Lens$ : $\BRegex \Leftrightarrow \BRegexAlt$} indicates that
$\Lens$ is a simple symmetric lens between $\LanguageOf{\BRegex}$ and
$\LanguageOf{\BRegexAlt}$. (Later, we will use undecorated variables for
stochastic regular expressions; we mark plain REs with overbars.)  When
clear from context, we shorten ``simple symmetric lens'' to just
``lens.''

@@

In contrast, the \Disconnect lens does not propagate any edits
from one format to the other.  It takes four arguments: two
regular expressions and two strings. The regular expressions specify the formats
of the corresponding data on the two sides while the strings provide default
values. 
%
\begin{lstlisting}
disconnect(salary, "", "unk", "") : salary $\Leftrightarrow$ ""
\end{lstlisting}
%
On creates, the input values are thrown away, and default values are
returned ($\CreateLOf{\StringAlt} =
\lstinline{"unk"}$), and on puts, the second argument is used and the first is
thrown away ($\PutROf{\String}{\StringAlt} = \StringAlt$). In our extended
example, the \lstinline{salary} field is only present in management files,
so we use the disconnect lens to ensure salary edits do not cause updates to the
HR file.
The defaults are strings that indicate the information is missing.

The insert \lstinline{ins} and delete \lstinline{del} lenses are
syntactic sugar for uses of the disconnect lens in which a string
constant is omitted entirely from the source and target formats,
respectively.
\begin{lstlisting}
 ins($t$) = disconnect("", $t$, "", $t$)
 del($s$) = disconnect($s$, "", $s$, "")
\end{lstlisting}

Finally, there are a number of combinators that compositionally construct
more complex lenses from simpler ones. These include concatenation
($\ConcatLensOf{\Lens_1}{\Lens_2}$ or $\Lens_1 . \Lens_2$), variation
($\OrLensOf{\Lens_1}{\Lens_2}$), and iteration ($\IterateLensOf{\Lens}$).
For example, the composite lens \lstinline{name_lens} in the running
example
%
\begin{lstlisting}
id(name) . id(" ") . id(name) . del(": ") . ins(",")
\end{lstlisting}
%
will transform ``\lstinline{Jane Doe: }'' to ``\lstinline{Jane Doe,}'' in
the forward direction (converting from the left format to the right).
\bcp{We don't actually give a nontrivial example of how disconnect works.}

@@

\begin{figure}
\begin{lstlisting}
let name_lens = id(name) . id(" ") . id(name) . del(": ") . ins(",") in
let employee_lens = name_lens . disconnect(salary,"","unk","") 
                                                    . disconnect("",company,"","UNK") in
let employees_lens = ins("\n") . employee_lens . iterate(id("\n") . employee_lens) in
ins(header) . employees_lens : emp_salaries $\Leftrightarrow$ emp_insurance
\end{lstlisting}
%\ksf{I don't think this is necesssary.}
%let emp_lens = or(id(""),employees_lens) in
  \caption{A lens that synchronizes management and HR employee files\bcp{I'm
    pretty sure there was an error in name\_lens: the thing between the two
    names should be id(" ") (was ins('','')).  Crossing my fingers that I'm
    making a correct fix...}}
  \label{fig:example_lens}
\end{figure}

@@

We provide typing rules for each of the simple symmetric combinators, most of
which are syntax directed. However, regular expressions have a number of
equivalences on them, and sometimes we must convert one regular expression type
to another, equivalent, regular expression type. Our typing rules include type
equivalence, so if a lens has type $\BRegex \Leftrightarrow \BRegexAlt$, then it
is also has type $\BRegex' \Leftrightarrow \BRegexAlt'$, where $\BRegex$ is
equivalent to $\BRegex'$, and $\BRegexAlt$ is equivalent to $\BRegexAlt'$. The
flexibility this type equivalence rule provides is useful when a different
representation of a regular expression would facilitate synthesis.

@@

While our example is relatively simple for demonstration, writing such lenses
for real-world formats is quite difficult, as these formats can be large and
represent data in complex and unintuitive ways. To alleviate the difficulty of
manually writing simple symmetric lenses, we wish to synthesize them instead.
Given a pair of regular expressions and a set of input-output examples, we want
to find a simple symmetric lens that is typed by the regular expression pair and
satisfies the input/output examples. We call such a lens a \emph{satisfying
  lens}. In our running example, we wish to synthesize a lens between
\lstinline{emp_salaries} and \lstinline{emp_insurance}, using as an input-output
example the data in Figure~\ref{fig:minimized-representations}. The algorithm
uses such examples to find suitable defaults for \Disconnect lenses and to
figure out how to match data that could be synchronised in multiple ways.

A challenge is that the simple symmetric lens combinators permit many
well-typed lenses
between a given pair of regular expressions. For example, 
Figure~\ref{fig:example_lens} gives one possible lens between regular
expressions  \lstinline{emp_salaries} and \lstinline{emp_insurance},
but 
%
\begin{lstlisting}
disconnect(emp_salaries,emp_insurance,rep(emp_salaries),rep(emp_insurance))
\end{lstlisting}
%
is another well-typed lens (where \lstinline{rep($\BRegex$)} denotes some string in the
language of $\BRegex$). Furthermore, adding the input-output example in
Figure~\ref{fig:minimized-representations} 
helps, but only a little: It may, in general, require {\em many} examples to rule
out all possible occurrences of nested \Disconnect lenses,
particularly in complex formats. 
%\ksf{I don't understand the following.  We shouldn't explain the issue in
%terms of \PutR and \PutL as we are focused on the combinators rather
%than the raw functions.}
%The default strings given to \Disconnect merely need to be the strings
%in the input-output examples, and the lens will still satisfy the
%specification.  While the disconnect lens is prohibited by two
%examples, or by a carefully chosen input-output example on \PutR
%or \PutL, this problem continues presenting itself for the sublenses,
%and is highlighted even more on larger formats.
While we could ask programmers to provide detailed and precise specifications
for their synthesis tasks, we would prefer an algorithm that can intelligently
choose a lens despite the underspecification. Instead of merely finding
\emph{any} satisfying lens, we wish to synthesize a satisfying lens that is
likely to please the user.

But what is a ``likely'' satisfying lens? We propose the following
heuristic: A satisfying
lens is more likely if it connects more data between the two
formats, \EG, by using an identity rather than a disconnect lens.  The
likeliest satisfying lenses would connect as much data as
possible. More formally, we define the likelihood of a
satisfying lens as the expected number of bits required to recover
data in one format from synchronized data in the other.  Higher
likelihoods correspond to lower numbers of bits. In more
detail, we say that two strings $s$ and $t$ are \emph{synchronized
according to lens $l$} if $l.\PutR\ s\ t = t$ and $l.\PutL\ t\ s = s$.\footnote{
The notation $l.\PutR$ extracts the \PutR function from simple
symmetric lens $l$; similarly for \PutL.}  We say that we
can \emph{recover} $s$ from $t$ using bits $b$ and lens $l$ if we can
reconstruct $s$ from $t$, $b$, and $l$.  For example, given
the \IdentityLens{} lens, we can recover $s$ from $t$ using no bits
because, in this case, $s$ is just $t$.  In contrast, given
the \Disconnect{} lens, we need enough bits to fully encode $s$ in
order to recover it from $t$ because $t$ contains no useful
information.  This calculation shows that if both \IdentityLens{}
and \Disconnect{} are satisfying lenses, then \IdentityLens{} is more
likely.

The expected number of bits required to recover data is the well-known
information-theoretic concept of the \emph{entropy} of the
data~\cite{Shannon1948}. Calculating entropy requires a probability distribution
over the space of possible values for the data. Specifically, given a set $S$
and a probability distribution $P \OfType S \rightarrow \Reals$ over $S$, the
entropy $\EntropyOf{S,P}$ is $-\Sigma_{s\in S}P(s)\Log_2P(s)$.

>>>>

  \centering
  \resizebox{\columnwidth}{!}{%
    \begin{tabular}{|>{\columncolor{vlightyellow}}c|>{\columncolor{vlightgreen}}c|}
      \hline
      Management's data & HR's data \\
      \hline
      \listingA & \listingB \\
      \hline
      \cellcolor{lightyellow}Management's type & 
      \cellcolor{lightgreen} HR's type\\
      \hline
      \cellcolor{lightyellow}\listingC & \cellcolor{lightgreen}\listingD \\
      \hline
    \end{tabular}
  }
  \caption{Hypothetical example data files and corresponding regular expressions
  used by management and HR at a US company to represent employee salaries and health
  insurance providers, respectively. \bcp{The colors are a bit loud,
    especially since there is so little color elsewhere.}
  %
  \bcp{Suggest replacing ``Name,Company'' with ``First Last, Company'' (too
    many ``name''s flying around)}
  %
  \bcp{More substantially, thinking about this example makes me wonder about
    a whole different way of specifying simple symmetric lenses: rather than
    just giving corresponding source and target pairs, could we give triples
    of the form ``new source / old target / new target'' and ``new target /
    old source / new source''?  I know these would be a bit more work to
    write, but they would also give the synthesis procedure way more
    information to work with---it seems to me it should be able to do much
    less guessing about where things are disconnected.  Would this allow us
    to drop all the information theory?  Or would we still need it?  (In
    retrospect, this seems like a fairly obvious thing to try, so it seems
    important to try it and report on how it performs relative to what we
    propose here...)}\afm{Oh sorry, yes we can write such examples.  I personally found that typically the same information could be provided through a series of 2 creates (aka: if we want a disconnect: creater a = b; creater a' = b:  if we want an identity: creater a = a; creater a' = a').  However, we also permit putr and putl examples of the proposed form in the tool 
Much like other aspects of the work, any situation with examples ultimately only constrains the subcomponents of the lens corresponding to that specific parse tree (aka: if I give an example about A in A|B, it only constrains "A").  I don't think it removes the need for the information theory, as all the other non-constrained subcomponents of the lens can still be "anything."
}  }
  \label{fig:minimized-representations}
\end{figure}

@@

\subsection{Simple Symmetric Lenses}
Semantically, a simple symmetric lens between sets $X$ and
$Y$ comprises four functions subject to four
``round-tripping'' laws:

%\begin{enumerate}
%\item $\CreateR \OfType \Regex \rightarrow \RegexAlt$
%\item $\CreateL \OfType \RegexAlt \rightarrow \Regex$
%\item $\PutR \OfType \Regex \rightarrow \RegexAlt \rightarrow \RegexAlt$
%\item $\PutL \OfType \RegexAlt \rightarrow \Regex \rightarrow \Regex$
%\end{enumerate}
\vskip 1.5ex
\begin{center}
\begin{minipage}[c]{.3\textwidth}
\begin{gather}
 \tag{1}
 \mbox{$\CreateR \OfType X \rightarrow Y$}\\
 \tag{2}
 \mbox{$\CreateL \OfType Y \rightarrow X$}\\
 \tag{3}
 \mbox{$\PutR \OfType X \rightarrow Y \rightarrow Y$}\\
 \tag{4}
 \mbox{$\PutL \OfType Y \rightarrow X \rightarrow X$}
\end{gather} 
\end{minipage} 
\hspace{.4in}
\begin{minipage}[c]{.5\textwidth}
\begin{align}
  \tag{\CreatePutRL}
  \PutLOf{(\CreateROf{x})}{x} = x\\
  \tag{\CreatePutLR}
  \PutROf{(\CreateLOf{y})}{y} = y\\
  \tag{\PutRL}
  \PutLOf{(\PutROf{x}{y})}{x} = x\\
  \tag{\PutLR}
  \PutROf{(\PutLOf{y}{x})}{y} = y
\end{align}
\end{minipage} 
\end{center}
\vskip 1ex
\bcp{Are we going to use the numbers next to the laws??  Seems like not, so
  why have them at all?}
\noindent
The two \KW{create} functions are used to propagate shared information and
fill in default values when introducing new data (\EG, the ``unk'' salary
entry is added\bcp{is added by what?  A create function, I guess, but the
  connection is not clear} alongside the name to the management file when HR inserts a
new employee). The two \KW{put} functions propagate edits from one format to
the other by combining a new value from one with an old value from the
other.  The round-tripping laws guarantee that pushing an ``un-edited''
value from one side (the result of a put or create) back through a lens in
the other direction will get back to exactly where we began.  \bcp{That
  paragraph seems likely to be quite opaque to any reader that is not
  already familiar with (symmetric) lenses.  How about a concrete example?}

@@

In principle, programmers can define simple symmetric lenses just by
writing four arbitrary functions by hand and showing they satisfy the round-tripping
laws.  But a better idea is to streamline the process by providing a set of
combinators---a domain-specific 
language---for building law-abiding complex lenses from simpler ones.  Such
bidirectional languages
have been given for building lenses over many different kinds of data,
including database relations~\cite{BohannonPierceVaughan} and algebraic data
types~\cite{symmetric-lenses}\bcp{and what else? graphs, etc.?}.  We focus
here on combinators for defining lenses between string data formats
described by regular expressions.

If $\BRegex$ and $\BRegexAlt$ are regular expressions, then
\lstinline{$\Lens$ : $\BRegex \Leftrightarrow \BRegexAlt$} indicates that
$\Lens$ is a simple symmetric lens between $\LanguageOf{\BRegex}$ and
$\LanguageOf{\BRegexAlt}$. (We will use undecorated variables later for
stochastic regular expressions; we mark plain REs with overbars.)  When
clear from context, we shorten ``simple symmetric lens'' to just
``lens.''

@@

In contrast, the \Disconnect lens does not propagate any edits at all
from one format to the other.  It takes four arguments: two
regular expressions and two strings. The regular expressions specify the formats
on the two sides, while the strings provide default values. 
%
\begin{lstlisting}
disconnect(salary, "", "unk", "") : salary $\Leftrightarrow$ ""
\end{lstlisting}
%
On creates, the input values are thrown away, and default values are
returned ($\CreateLOf{\StringAlt} =
\lstinline{"unk"}$), and on puts, the second argument is used and the first is
thrown away ($\PutROf{\String}{\StringAlt} = \StringAlt$). In our extended
example, the \lstinline{salary} field is only present in management files,
so we use the disconnect lens to ensure salary edits do not cause updates to the
HR file.
The defaults are strings that indicate the information is missing.

The insert lens \lstinline{ins} and the delete lens \lstinline{del} are
syntactic sugar for uses of the disconnect lens in which a string
constant is omitted entirely from the source or target format.
\begin{lstlisting}
 ins($t$) = disconnect("", $t$, "", $t$)
 del($s$) = disconnect($s$, "", $s$, "")
\end{lstlisting}
The \lstinline{ins} lens inserts a constant string when going from
left to right, while \lstinline{del} inserts a string when going from right
to left.

Finally, there are a number of combinators that construct
more complex lenses from simpler ones. These include concatenation
($\ConcatLensOf{\Lens_1}{\Lens_2}$, often written $\Lens_1 . \Lens_2$), variation
($\OrLensOf{\Lens_1}{\Lens_2}$), and iteration ($\IterateLensOf{\Lens}$).
For example, the composite lens \lstinline{name_lens} in the running
example
%
\begin{lstlisting}
id(name) . id(" ") . id(name) . del(": ") . ins(",")
\end{lstlisting}
%
will transform ``\lstinline{Jane Doe: }'' to ``\lstinline{Jane Doe,}'' in
the left-to-right direction.
\bcp{We don't actually give a nontrivial example of how disconnect works.}

@@

\begin{figure}
\begin{lstlisting}
let name_lens = id(name) . id(" ") . id(name) . del(": ") . ins(",") in
let employee_lens = name_lens . disconnect(salary,"","unk","") 
                                                    . disconnect("",company,"","UNK") in
let employees_lens = ins("\n") . employee_lens . iterate(id("\n") . employee_lens) in
ins(header) . employees_lens : emp_salaries $\Leftrightarrow$ emp_insurance
\end{lstlisting}
%\ksf{I don't think this is necesssary.}
%let emp_lens = or(id(""),employees_lens) in
  \caption{A lens that synchronizes management and HR employee files\bcp{I'm
    pretty sure there was an error in name\_lens: the thing between the two
    names should be id(" ") (it was ins('','')).  Crossing my fingers that I'm
    making a correct fix...}}
  \label{fig:example_lens}
\end{figure}

@@

We provide typing rules for the simple symmetric combinators, most of
them syntax directed. However, regular expressions have a number of
equivalences on them, and sometimes we must convert one regular expression type
to another, equivalent, regular expression type. \bcp{The next sentence is
  dense.  Just show the rule?}Our typing rules include type
equivalence, so if a lens has type $\BRegex \Leftrightarrow \BRegexAlt$, then it
is also has type $\BRegex' \Leftrightarrow \BRegexAlt'$, where $\BRegex$ is
equivalent to $\BRegex'$, and $\BRegexAlt$ is equivalent to
$\BRegexAlt'$. \bcp{We're not talking about synthesis yet, so this next
  sentence seems off-track.  Drop it?}The
flexibility this type equivalence rule provides is useful when a different
representation of a regular expression would facilitate synthesis.

@@

Lens expressions for small examples like the one above are pretty easy to
write.  But for larger and more complex formats, it can become quite difficult to
write lenses by hand.  Instead, we wish to synthesize them from examples.

That is, given a pair of regular expressions and a set of input-output examples, we want
to find a simple symmetric lens that is typed by the regular expression pair and
satisfies all the input/output examples. We call such a lens a \emph{satisfying
  lens}. In our running example, we wish to synthesize a lens between
\lstinline{emp_salaries} and \lstinline{emp_insurance}, using as an input-output
example the data in Figure~\ref{fig:minimized-representations}.
\bcp{Suggest deleting this sentence:}The algorithm
uses such examples to find suitable defaults for \Disconnect lenses and to
figure out how to match data that could be synchronised in multiple ways.

One challenge is that the simple symmetric lens combinators permit many
well-typed lenses
between a given pair of regular expressions. For example, 
Figure~\ref{fig:example_lens} gives one possible lens between regular
expressions  \lstinline{emp_salaries} and \lstinline{emp_insurance},
but 
%
\begin{lstlisting}
disconnect(emp_salaries, emp_insurance, rep(emp_salaries), rep(emp_insurance))
\end{lstlisting}
%
is another well-typed lens (where \lstinline{rep($\BRegex$)} denotes some string in the
language of $\BRegex$).  Adding the input-output example in
Figure~\ref{fig:minimized-representations} 
helps, but only a little: In general, {\em many} examples may be required to rule
out all possible occurrences of nested \Disconnect lenses,
particularly in complex formats. 
%\ksf{I don't understand the following.  We shouldn't explain the issue in
%terms of \PutR and \PutL as we are focused on the combinators rather
%than the raw functions.}
%The default strings given to \Disconnect merely need to be the strings
%in the input-output examples, and the lens will still satisfy the
%specification.  While the disconnect lens is prohibited by two
%examples, or by a carefully chosen input-output example on \PutR
%or \PutL, this problem continues presenting itself for the sublenses,
%and is highlighted even more on larger formats.
While we could ask programmers to provide detailed and precise specifications
for their synthesis tasks, we would prefer an algorithm that can intelligently
choose a lens despite the underspecification. Instead of merely finding
\emph{any} satisfying lens, we wish to synthesize a satisfying lens that is
likely to please the user.

How can we identify such a ``likely'' lens? We propose the following
heuristic: A satisfying
lens is ``more likely'' if it ``connects'' more data between the two
formats, \EG, by using an identity rather than a disconnect lens.  The
likeliest satisfying lenses would connect as much data as
possible. More formally, we define the likelihood of a
satisfying lens as the expected number of bits required to recover
data in one format from synchronized data in the other.  Higher
likelihoods correspond to fewer bits. Yet more formally, we say that two
strings $s$ and $t$ are \emph{synchronized 
according to lens $l$} if $l.\PutR\ s\ t = t$ and $l.\PutL\ t\ s = s$.\footnote{
The notation $l.\PutR$ extracts the \PutR function from simple
symmetric lens $l$; similarly for \PutL.\bcp{Let's introduce this notation
  earlier when talking about lenses; shoving it in a footnote here is clunky.}}  We say that we
can \emph{recover} $s$ from $t$ using bits $b$ and lens $l$ if we can
reconstruct $s$ from $t$, $b$, and $l$.  For example, given
the \IdentityLens{} lens, we can recover $s$ from $t$ using no bits
because, in this case, $s$ is just $t$.  In contrast, given
the \Disconnect{} lens, we need enough bits to fully encode $s$ in
order to recover it from $t$ because $t$ contains no useful
information.  Thus, if both \IdentityLens{}
and \Disconnect{} are satisfying lenses for a particular pair of formats,
then \IdentityLens{} will be more likely.

The expected number of bits required to recover a piece of data corresponds
to the well-known information-theoretic concept of
\emph{entropy}~\cite{Shannon1948}. Calculating entropy requires a
probability distribution over the space of possible values for the
data. Specifically, given a set $S$ and a probability distribution
$P \OfType S \rightarrow \Reals$ over $S$, the entropy $\EntropyOf{S,P}$ is
$-\Sigma_{s\in S}P(s)\Log_2P(s)$.  \bcp{That definition requires some more words of
  explanation!  And probably an example or two.  It is fundamental to the
  rest of the paper: if a reader doesn't follow it, they will be lost.  (I
  am a little lost myself... is entropy a property of an individual piece of
  data (as the wording above suggests), or is it a property of the set to
  which the data belongs?)}
